---
title: "Machine Learning Notes"
output: html_document
---

```{r setup, cache = F, echo = F, message = F, warning = F, tidy = F}
```

*This documents collects some notes and code from the Coursera course [practical machine learning](https://class.coursera.org/predmachlearn-003)*.

The [*caret*](http://caret.r-forge.r-project.org/) package (short for Classification And REgression Training) is a set of functions that attempt to streamline the process for creating predictive models. The package contains tools for:

* data splitting
* pre-processing
* feature selection
* model tuning using resampling
* variable importance estimation

## Data splitting

We can do the *data splitting*
```{r loadPackage}
library(lattice); library(ggplot2);
library(caret); library(kernlab); 
data(spam)
inTrain <- createDataPartition(y=spam$type, p = 0.75, list = FALSE) # 75% for train and 25% for test
training <- spam[inTrain,]
testing <- spam[-inTrain,]
dim(training)
```

We can also split the data with *K-fold*
```{r kfold,dependson="loadPackage"}
set.seed(32323)
folds <- createFolds(y=spam$type, k=10, list=TRUE, returnTrain=TRUE)
sapply(folds,length)
folds[[1]][1:10]
```



Or *fit a model*
```{r training, dependson="loadPackage",cache=TRUE, warning = F}
set.seed(32343)
modelFit <- train(type ~ ., data = training, method = "glm")
modelFit
```

The final model is
```{r}
modelFit$finalModel
```

We can now predict
```{r predictions, dependson="training",cache=TRUE}
predictions <- predict(modelFit,newdata=testing)
head(predictions)
```

The confusion matrix is 
```{r confusion, dependson="predictions",cache=TRUE}
confusionMatrix(predictions,testing$type)
```

